Milestone 2

### 2022-10-03 Milestone2.Rmd
Worked on Milestone2 together

Milestone 2

```{r, echo=FALSE}
library(readxl)
library(tidyr)
library(lubridate)

@@

•	Description of dataset
o	What is the data source? (1-2 sentences on where the data is coming from, dates included, etc.)
o	How does the dataset relate to the group problem statement and question?

@@

@@

@@

>>>>

---
title: "Milestone 2"
names: "Dawson Coblin & Jose Lazo"
date: "October 3, 2022"
output: 
---
```{r, echo=FALSE}
library(readxl)
library(tidyr)
library(lubridate)

@@

Description of dataset

o	What is the data source? (1-2 sentences on where the data is coming from, dates included, etc.)
The monkeypox data file contains information on the number of monkeypox cases reported by EU/EEA countries or collected throughout epidemiologic intelligence at ECDC. 
Each row contains the corresponding data for a country, day of reporting, number of cases and source of information (data are in long format). The file is updated twice a week. The date range for this data set is from 05/09/22 - 08/23/22

o	How does the dataset relate to the group problem statement and question?
For our project we are interested in understanding how case rates may differ by region and various demographic factors. The MPX data has information on confirmed cases by countries.

@@

Import process
1) Download zip file from phw251_projectdata
2) Set up our github repository on our R datahub
3) One team member uploaded pertinent excel files to their Rproject 251
4) Commit and push to have excel files on our team's github

@@

```{r}
str(MPX_data)
mean(MPX_data$ConfCases)
```
/newpage

@@

Confcases is a numeric data element
```{r}
round(mean(MPX_data$ConfCases),2)
median(MPX_data$ConfCases)
range(MPX_data$ConfCases)
```
Mean = 5.72
Median = 0
Range = 0,655

DateRep 
Is a character variable which contains dates 05/09/22 through 08/23/22. We will convert this data into numeric form.

```{r}
unique(MPX_data$CountryExp)
```

CountryExp
Is a character variable which contains 29 countries listed above.

```{r}
unique(MPX_data$CountryCode)
```

CountryCode
Is a character with the 2 letter abbreviation of countries with 29 values which matches with CountryExp

```{r}
unique(MPX_data$Source)
```

Source is a character variable with 2 options, TESSy and EI
